% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{fontawesome}
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{graphicx}

% \renewcommand{\baselinestretch}{0.95}  % 压缩行距
% \footnotesize  % 字体大小
\setlength{\parskip}{0pt}  % 去除段落间空行

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\centerline{\huge \bf Dedan Chen}
\vspace{1ex}
\centerline{
    \small \faEnvelope~13917374906@163.com \quad \faPhone~(+86) 139-1737-4906 \quad \faGithub~\href{https://github.com/rosesnack}{rosesnack}
}


\section{\bf EDUCATION}

\datedsubsection{\textbf{Nanjing University}}{Sep. 2022 -- Jun. 2026(Expected)}
B.S. in Computer Science \& Technology \hfill Nanjing, China

\begin{itemize}
    \item  \textbf{GPA}: 4.56/5.0
    \item \textbf{Scholarships}: Tencent Scholarship, Huawei Scholarship
    \item \textbf{Core Curriculums}: Data Structures, Operating Systems, Foundations of Computer Networks, Algorithm Design \& Analysis, Introduction to Databases, Introduction to Computer Systems, Advanced Programming
\end{itemize}


\section{\bf PROJECT EXPERIENCE}

\datedsubsection{\textbf{Class Survivor Game (Advanced Programming Course Project)}}{Apr. 2023 -- Jun. 2023}
\begin{itemize}
    \item Built a 2D action game using Qt framework and C++, featuring player control, item/upgrade systems, multiple enemy behaviors, and a polished interface designed with Qt’s graphical components.
    \item Leveraged Qt's signal-slot mechanism and C++'s object-oriented features (inheritance, polymorphism) to structure flexible and maintainable game logic.
\end{itemize}

\datedsubsection{\textbf{Fundamentals of Computer Systems-PA}}{Sep. 2023 -- Jan. 2024}
\begin{itemize}
    \item Based on the framework code, implemented a complete computer system NEMU, including i386 instruction set, memory management, paging and segmentation mechanism, exception and interrupt, etc.
\end{itemize}

\datedsubsection{\textbf{Huawei Shengsi MindSpore Innovation Training Camp}}{Aug. 2025}
\begin{itemize}
    \item Awarded \textbf{First Prize} as part of a team in an AI model development competition hosted by Huawei.
    \item Built a medical Q\&A chatbot using a fine-tuned GPT-2 model using the MindSpore platform, capable of generating effective medical responses based on user-described symptoms.
\end{itemize}


\section{\bf RESEARCH EXPERIENCE}

\datedsubsection{\textbf{Research on Sentiment Analysis Technology Based on Transformer}}{Dec. 2023 -- Dec. 2024}
\begin{itemize}
    \item Constructed an academic sentiment classification model using 4,000 manually labeled forum texts, identifying both traditional polarity and three types of academic emotions.
    \item Fine-tuned BERT model achieved F1-scores of 0.795 (academic emotions) and 0.785 (emotional polarity) via five-fold cross-validation. The model was used for sentiment monitoring on the openEuler forum to support user engagement analysis.


    \item Integrated Span-ASTE-tool to extract (Aspect, Opinion, Sentiment) triples, enabling deeper analysis of user satisfaction and community climate.
\end{itemize}

\datedsubsection{\textbf{Contributor Profiling and Recommendation}}{Sep. 2024 -- Jan. 2025}
\begin{itemize}
    \item Built a Random Forest model to recommend potential contributors for open-source projects by analyzing users' past GitHub activities (e.g., PRs, pushes).
\end{itemize}



\section{\bf INTERNSHIP EXPERIENCE}

\datedsubsection{\textbf{Microsoft Corporation}}{Jan. 2025 - Mar. 2025}
C + AI China Center One Intern \hfill Beijing, China
\begin{itemize}
  \item  \textbf{C\# Code Development}: Participated in the development of the virtual human interaction system's C\# code, including real-time audio stream processing, interaction with OpenAI models, and speech synthesis control. Used the OpenAI RealtimeConversation API for real-time dialogue interaction and added fault recovery features to enhance the product experience.
  \item \textbf{Prompt Improvement}: Improved the virtual human interaction prompts based on continuous testing and customer feedback, ensuring they better align with the character profile and company background.
\end{itemize}



\section{\bf SKILLS}
\begin{itemize}
  \item \textbf{Programming Languages:} Proficient in C++, Python; Familiar with Java, C\#, SQL
  \item \textbf{Techniques \& Tools:} Linux, PyTorch, Git, LaTeX, MySQL
\end{itemize}


\end{document}
